Towards the Development of an Intelligent Building Energy Management System -- iBEMS \thanks{The results presented in this paper were produced by a group of senior undergraduate students: Brian Lauer and Elliot Watkins }

### 2021-09-24 paperIEEE-IECON2021.tex
Changed case of agents in paper

\section{Software Implementation}
\label{sec:SoftwareImplementation}
The Flask web server is built using a Python web framework titled Flask which
allows programmers to develop a dynamic web server capable of rendering data to
HTML pages. The benefit of this framework over other Python web frameworks like
Django is the large amount of customization available. For example, the
developers can create a completely custom user login system. For now, the server
is capable of being accessed only on the server computer running Ubuntu Linux.
In the future, support could be added to allow any user on the LAN to access the
web server. Other web frameworks use object relational mapping directly to
access the relevant databases. However, the current iBEMS uses direct queries with both
SQLite and the Cassandra query language to query the databases. We used
2 different databases to store information on. The Apache Cassandra database was
better suited for the time series data such as device status and power usage.
This database was therefore utilized a lot by the Control and Scheduling Agents.
The SQLite database hold parameters that do not change over time like device
ID's, IP addresses, and MAC addresses which made it amendable to the processes
in the Discovery Agent. The first agent that is
used by the iBEMS Core on startup is the discovery agent. It is responsible for
reaching out on the network and finding all devices that the iBEMS Core has
support for. This process involves retrieving the following parameters: IP
address, Port number, MAC address, Manufacturer, Name, and API. Once all
available devices are connected, the Control agent is used to change the status
of each device and collect power usage data in real time. Finally, the
scheduling will take input from the user and place the corresponding scheduling
periods in the Apache Cassandra database. Then, a thread is created to poll the
current device status at regular intervals and update the status if it does not
match the defined status in the Apache Cassandra database.

>>>>

\section{Software Implementation}
\label{sec:SoftwareImplementation}
The Flask web server is built using a Python web framework titled Flask which
allows programmers to develop a dynamic web server capable of rendering data to
HTML pages. The benefit of this framework over other Python web frameworks like
Django is the large amount of customization available. For example, the
developers can create a completely custom user login system. For now, the server
is capable of being accessed only on the server computer running Ubuntu Linux.
In the future, support could be added to allow any user on the LAN to access the
web server. Other web frameworks use object relational mapping directly to
access the relevant databases. However, the current iBEMS uses direct queries with both
SQLite and the Cassandra query language to query the databases. We used
2 different databases to store information on. The Apache Cassandra database was
better suited for the time series data such as device status and power usage.
This database was therefore utilized a lot by the control and scheduling agents.
The SQLite database hold parameters that do not change over time like device
ID's, IP (Internet Protocol) addresses, and MAC addresses which made it amendable to the processes
in the discovery agent. The first agent that is
used by the iBEMS Core on startup is the discovery agent. It is responsible for
reaching out on the network and finding all devices that the iBEMS Core has
support for. This process involves retrieving the following parameters: IP
address, Port number, MAC address, Manufacturer, Name, and API. The discovery agent accomplishes this by cycling through all the API modules and calls the corresponding discovery method. IP multicasting via UDP (User Datagram Protocol) is used for finding all devices that respond to a specific multicast group and port. The device's local IP address can be obtained from the response and stored in the metadata database which can allow the system to obtain information from the device later on. Once all
available devices are connected, the control agent is used to change the status
of each device and collect power usage data in real time. Finally, the
scheduling will take input from the user and place the corresponding scheduling
periods in the Apache Cassandra database. Then, a thread is created to poll the
current device status at regular intervals and update the status if it does not
match the defined status in the Apache Cassandra database.
